### 2024-10-20 src/Submission.Rnw
Added ranking of variables by correlation coefficient

>>>>

\section{Ranking the variables based on the correlation coefficient}
<<echo=TRUE>>=
# List of predictor variables (excluding the target variable)
predictor_vars <- c("age", "sex", "bmi", "bp", "s1", "s2", "s3", "s4", "s5", "s6")

# Calculate the correlation between each predictor and the target
correlations <- sapply(predictor_vars, function(var) {
  cor(diabetes[[var]], diabetes$target)
})

# Print the correlation coefficients
correlations

# Rank variables by absolute correlation
correlations_sorted <- sort(abs(correlations), decreasing = TRUE)

# Print the ranked correlations
correlations_sorted
@
This shows the most important variable is BMI, followed by possibly log of serum triglycerides level, and the blood pressure, which is a common factor in diabetes progression. The least important variable is gender as diabetes can manifest in any gender and makes it an irrelevant variable with minimal contribution to the dataset but more for record keep purposes.
